Relating games of Menger, countable fan tightness, and selective separability

### 2016-10-15 articles/relating-games-menger-cft-ss/article.tex
slick strategic<=>Markov generalization

@@

In this notation,
Barman and Dow showed that \(SS\) does not imply
\(SS^+\). We aim to make progress on the following question attributed to
Gary Gruenhage:

@@

The solution is known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerGamePreprint} the author showed that while \(M^+\) implies
\(M^{+mark}\) for second-countable spaces, there exists a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\).

@@

\begin{proof}
  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
  \[
    \mc U_n(B)
      =
    \left\{
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
    :
      \vec x\in B
    \right\}
  .\]
  Consider the finite set \(F\in[X]^{<\omega}\). Since
  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
  It follows that \(F\subseteq x^{-1}[(-1,1)]\in\mc U_n(B)\),
  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).

@@

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

@@

  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \vec 0
      \in
    \cl{\bigcup_{n<\omega} \sigma(D(\mc U_n),n)}
  .\]
  Now let
  \[
    \tau(\mc U_n,n)
      =
    \{
      U_{\vec y,\mc U_n}
    :
      \vec y \in \sigma(D(\mc U_n),n)
    \}
      \in
    [\mc U_n]^{<\omega}
  .\]
  We claim that \(\bigcup_{n<\omega}\tau(\mc U_n,n)\)
  is an \(\omega\)-cover.
  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
  contains some point \(\vec y\in \sigma(D(\mc U_n),n)\)
  for some \(n<\omega\). It follows
  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\mc U_n,n)\).
\end{proof}

@@

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact is simply the fact that its countably infinite subsets
  are closed and discrete.
  We define the strategy \(\sigma\) for \(\plII\) in
  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.

@@

  For \(n<\omega\)
  let \(\sigma_n(\<\mc U_n\>)=\{I_n\}\)
  where \(I_n\) is a co-countable set containing \(\infty\).
  Denote
  \(\onePtLind{\omega_1}\setminus I_n=\{\alpha_{n,m}:m<\omega\}\),
  and then for \(m<\omega\)
  let \(\sigma_n(\<\mc U_n,\dots,\mc U_{n+m}\>)\) contain exactly
  one set, a superset of \(\{\infty\}\cup\{\alpha_{i,j}:i\leq n,j\leq n+m\}\).

  TODO: finish
\end{proof}

>>>>

\renewcommand{\vec}{\mathbf}

@@

In this notation,
Barman and Dow showed that \(SS\) does not imply
\(SS^+\). Our goal is to make progress on the following question
attributed to Gary Gruenhage:

@@

The solution is already known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerGamePreprint} the author showed that while \(M^+\) implies
\(M^{+mark}\) for second-countable spaces, there exists a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\).

@@

\begin{proof}
  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
  \[
    \mc U_n(B)
      =
    \left\{
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
    :
      \vec x\in B
    \right\}
  .\]
  Consider the finite set \(F\in[X]^{<\omega}\). Since
  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
  It follows that \(F\subseteq x^{\leftarrow}[(-1,1)]\in\mc U_n(B)\),
  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).

@@

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

@@

  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \vec 0
      \in
    \cl{\bigcup_{n<\omega} \sigma(D(\mc U_n),n)}
  .\]
  Now let
  \[
    \tau(\mc U_n,n)
      =
    \{
      U_{\vec y,\mc U_n}
    :
      \vec y \in \sigma(D(\mc U_n),n)
    \}
      \in
    [\mc U_n]^{<\omega}S
  .\]
  We claim that \(\bigcup_{n<\omega}\tau(\mc U_n,n)\)
  is an \(\omega\)-cover.
  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
  contains some point \(\vec y\in \sigma(D(\mc U_n),n)\)
  for some \(n<\omega\). It follows
  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\mc U_n,n)\).
\end{proof}

@@

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
  is simply the fact that its countably infinite subsets
  are closed and discrete.
  We define the strategy \(\sigma\) for \(\plII\) in
  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.

@@

  For \(n<\omega\)
  let \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\),
  where
  \[
    U(\<\mc U_0,\dots,\mc U_n\>)
      =
    \onePtLind{\omega_1}
      \setminus
    \{\alpha_{n,m}:m<\omega\}
  \]
  is a co-countable set
  containing \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\).

  Consider the arbitrary sequence of moves \(\<\mc U_0,\mc U_1,\dots\>\)
  by \(\plI\). For \(F\in[\onePtLind{\omega_1}]^{<\omega}\), choose
  \(n<\omega\) such that
  \[
    F\cap\{\alpha_{i,j}:i,j<\omega\}
      =
    F\cap\{\alpha_{i,j}:i,j<n\}
      \subseteq
    U(\<\mc U_0,\dots,\mc U_n\>)
  \]
  It follows that as
  \[
    F
      \setminus
    \{\alpha_{i,j}:i,j<\omega\}
      \subseteq
    F
      \setminus
    \{\alpha_{n,m}:m<\omega\}
      \subseteq
    U(\<\mc U_0,\dots,\mc U_n\>)
  \]
  \(F\) is a subset of
  \(U(\<\mc U_0,\dots,\mc U_n\>)\), making
  \(
    \bigcup_{n<\omega}
    \sigma(\<\mc U_0,\dots,\mc U_n\>)
  \)
  an \(\omega\)-cover.
\end{proof}

\begin{corollary}
  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{+mark}\).
\end{corollary}

If \(C_p(\onePtLind{\omega_1})\) were separable, it would be a negative
solution to Question \ref{mainQuestion}. However, it is not.

\begin{lemma}[\cite{MR953314}]
  For a \(T_{3\frac{1}{2}}\) topological space \(X\),
  \(C_p(X)\) is separable if and only if \(X\) has a coarser separable
  metrizable topology.
\end{lemma}

\begin{corollary}
  \(C_p(\onePtLind{\omega_1})\) is not separable.
\end{corollary}

\begin{proof}
  Every metrizable topological space has points \(G_\delta\).
  However, if every neighborhood of \(\infty\) is
  co-countable, \(\{\infty\}\) cannot be the intersection of countably many
  open sets.
\end{proof}

% It's easily seen that \(CFT^+\) is a hereditary property for all subspaces.

\section{Equivalence of certain strategic and Markov seleciton properties}

Barman and Dow
previously demonstrated that \(SS^+\) is equivalent to
\(SS^{+mark}\) amongst countable spaces.
A similar result by the author
showed that \(M^+\) is equivalent to \(M^{+mark}\) in second-countable
spaces. The following result generalizes both.

\begin{lemma}\label{mainLemma}
  Let \(\mc A\) be a family of sets where
  \(|\bigcup\mc A|\leq\omega\)
  and let \(\mc B\) be a family of sets closed under supersets. Then
  \(\plII\win\schSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\).
\end{lemma}

\begin{proof}
  Let \(\sigma\) witness \(\plII\win\schSelGame{\mc A}{\mc B}\).

  For \(t\in\omega^{<\omega}\), suppose
  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
      \subseteq
    [\bigcup\mc A]^{<\omega}
  \)
  and therefore is countable.
  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
  \(
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
      =
    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
  \).

  Let \(b:\omega\to\omega^{<\omega}\) be a bijection,
  and define
  \(\tau(A,n)=\sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A\>)\).
  Consider \(\<A_0,A_1,\dots\>\in\mc A^\omega\).

  Define \(f\in\omega^\omega\) as follows.
  Let \(n<\omega\) and suppose that \(f\rest n\) has been already
  been defined. Then choose \(f(n)<\omega\) such that
  \(
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},A_{b^{\leftarrow}(f\rest n)}\>)
      =
    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},Z_{f\rest (n+1)}\>)
  \).

  Since \(\<Z_{f\rest1},Z_{f\rest2},\dots\>\in\mc A^\omega\), it follows
  that
  \(
    \bigcup_{n<\omega}\sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n}\>)
      \in
    \mc B
  \).
  The result then follows from
  \begin{align*}
    \bigcup_{n<\omega}\tau(A_n,n)
      & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & \supseteq
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & =
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},A_{b^{\leftarrow}(f\rest|b(n)|)}\>)
      \\ & =
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},Z_{f\rest(|b(n)|+1)}\>)
      \\ & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest n}\>)
      \\ & \in
    \mc B
  \end{align*}
  as \(\mc B\) is closed under supersets.
\end{proof}

\begin{corollary}[\cite{MR2868880}]
  A countable space \(X\) is \(SS^+\) if and only if it is
  \(SS^{+mark}\).
\end{corollary}

\begin{proof}
  \(\bigcup\mc D_X=X\) is countable, and any set containing a dense
  set is dense.
\end{proof}

\begin{corollary}
  A second-countable space \(X\) is \(\Omega M^+\) if and only if
  it is \(\Omega M^{+mark}\).
\end{corollary}

\begin{proof}
  First note that any witness for
  \(\Omega M^+\) is a witness for
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).
  Fix a countable base \(\mc B\) for \(X\) closed under finite unions, and let
  \(\Omega_X^*\) be the collection of \(\omega\)-covers of \(X\) which only
  use basic open sets. Then
  \(\bigcup\Omega_X^*=\mc B\) is countable, and any set containing an
  \(\omega\)-cover is an \(\omega\)-cover; therefore
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\) if and only if
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).

  So let \(\sigma\) witness
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).
  For each \(\omega\)-cover \(\mc U\) and finite set \(F\in[X]^{<\omega}\),
  choose \(U_{\mc U,F}\in\mc U\) such that \(F\subseteq U\). Then choose a
  basic open set \(U_{\mc U,F}^*\) such that
  \(F\subseteq U_{\mc U,F}^*\subseteq U_{\mc U,F}\). Finally, for each
  \(\omega\)-cover \(\mc U\), let
  \[
    \mc U^*
      =
    \{
      U_{\mc U,F}^*
        :
      F\in[X]^{<\omega}
    \}
      \in
    \Omega_X^*
  .\]

  Define the strategy \(\tau\) such that
  \(\tau(\mc U,n)=\{U_{\mc U,F}:U_{\mc U,F}^*\in\sigma(\mc U^*,n)\}\).
  For any sequence of \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\),
  it follows that \(\bigcup_{n<\omega}\sigma(\mc U_n^*,n)\) is an
  \(\omega\)-cover, and therefore
  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also.
\end{proof}

\begin{corollary}[\cite{clontzMengerGamePreprint}]
  A second-countable space \(X\) is \(M^+\) if and only if
  it is \(M^{+mark}\).
\end{corollary}

\begin{proof}
  An easy adapatation of the preceding proof, replacing \(\omega\)-covers
  with open covers, and replacing \(F\in[X]^{<\omega}\) with \(x\in X\).
\end{proof}

\section{Acknowledgements}
The author would like to thank Ziqin Feng for his helpful comments on
this topic during
the 31st Summer Conference on Topology and its Applications.
